Generalised gravitational burst generation with Generative Adversarial Networks

### 2021-01-28 Paper_draft/main.tex
Updated abstract

\begin{abstract}
We introduce the use of conditional generative adversarial networks for generalised GW burst generation in the time domain. Generative adversarial networks are generative machine learning models that produce new data based on the statistics of the training set. We condition the network on five classes of time-series signals: sine-Gaussian, ringdown, white noise burst, Gaussian pulse and binary black hole merger and show that the model can replicate the features of these classes. Additionally, we show the model can produce generalised burst signals through interpolation and class mixing. Furthermore, we build a convolutional neural network classifier to predict the detectability of these newly produced signals in LIGO detector noise against more traditional burst waveforms. 
\end{abstract}

@@

% introduce the training data
%
\begin{figure}
    \centering
    \showthe\textwidth
    \includegraphics[width=\textwidth]{figures/training-sample.pdf}
    \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study. Values of the parameters were selected randomly from uniform distributions from \cref{Tab:training_parms}.}
    \label{fig:training_waveforms}
\end{figure}
% introduce the signal models
%
We propose a signal generation scheme using a \ac{CGAN} trained on burst-like waveforms. We call this \texttt{McGANn}\footnote{https://github.com/jmcginn/McGANn} and it is a \ac{CGAN} trained on five signal classes each spanning a range of prior signal parameters. The signal classes are:

>>>>

\begin{abstract}
We introduce the use of conditional generative adversarial networks for generalised gravitational wave burst generation in the time domain. Generative adversarial networks are generative machine learning models that produce new data based on the features of the training data set. We condition the network on five classes of time-series signals that are often used to characterise gravitational wave burst searches: sine-Gaussian, ringdown, white noise burst, Gaussian pulse and binary black hole merger. We show that the model can replicate the features of these standard signal classes and, in addition, produce generalised burst signals through interpolation and class mixing. We also present an example application where a convolutional neural network classifier is trained on burst signals generated by our conditional generative adversarial network. We show that a convolutional neural network classifier trained only on the standard five signal classes has a poorer detection efficiency than a convolutional neural network classifier trained on a population of generalised burst signals drawn from the entire signal class space.
\end{abstract}

@@

% introduce the training data
%
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/training-sample.pdf}
    \caption{Examples of the five different waveforms that were used in training the \ac{GAN} for this study. Values of the parameters were selected randomly from uniform distributions from \cref{Tab:training_parms}.}
    \label{fig:training_waveforms}
\end{figure}
% introduce the signal models
%
We propose a signal generation scheme using a \ac{CGAN} trained on burst-like waveforms. We call this \texttt{McGANn}\footnote{https://github.com/jmcginn/McGANn} and it is a \ac{CGAN} trained on five signal classes each spanning a range of prior signal parameters. The signal classes are:
